HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN

### 2020-04-23 cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
not testing institution for model sel

## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain effective count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}

@@

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "(1|Reported_Gender)", "scale(PMI)",
                                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```

>>>>

## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(mvBIC)

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='mvBIC-all-cohorts')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain effective count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}

@@

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = COVARIATES,
                         variables = array(c("(1|Reported_Gender)", "scale(PMI)",
                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```
